---
output: md_document
---

# Awesome statistics [![Awesome](https://cdn.rawgit.com/sindresorhus/awesome/d7305f38d29fed78fa85652e3a63e154dd8e8829/media/badge.svg)](https://github.com/sindresorhus/awesome)

```{r include=FALSE}
knitr::opts_chunk$set(comment = NULL)
```

```{r introCode, echo=FALSE, message=FALSE, warning=FALSE}
library("tidyverse")
library("kableExtra")
df_raw <- read_csv("data.csv")
df <- df_raw |> 
  filter(dead == 0, awesome == 1) |> 
   transmute(title = paste0("[", title, "](", url, ")"), category)

```

The repository consists of a dataset with curated links to material dealing with statistics and data. There is a total of `r NROW(df_raw[df_raw$dead == 0,])` active links in the dataset. The `r NROW(df_raw[df_raw$awesome == 1 & df_raw$dead == 0,])` awesome/recommended links in the dataset are listed below. Feel free to add additional links to the dataset.

# Books

```{r generateTableBooks, echo=FALSE, message=FALSE, warning=FALSE}

df |> 
  filter(category == "books") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# General

```{r generateTableGeneral, echo=FALSE, message=FALSE, warning=FALSE}

df |> 
  filter(category == "general") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Distributions

```{r generateTableDistribution, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "distribution") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Analysis

## Hypothesis testing

```{r generateTableHypothesis, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "hypothesis") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Correlation

```{r generateTableCorrelation, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "correlation") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Spatial

```{r generateTableSpatial, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "spatial") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Regression

```{r generateTableRegression, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "regression") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Bayesian

```{r generateTableBayesian, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "Bayesian") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Meta-analysis

```{r generateTableMetaanalysis, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "metaanalysis") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Hierarchical modeling

```{r generateTableMultilevel, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "multilevel") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```


## Experiments

```{r generateTableExperiments, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "experiments") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Data visualisation

```{r generateTableViz, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "visualisation") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```


# Data

## General

```{r generateTableData, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "data") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Missing data

```{r generateTableMissingData, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "missingdata") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Sample size

```{r generateTableSamplesize, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "samplesize") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Datasets

```{r generateTableDatasets, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "dataset") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Statistical software

## General

```{r generateTableSoftware, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "software") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## R

```{r generateTableR, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "R") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Python

```{r generateTablePython, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "Python") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Stata

```{r generateTableStata, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "Stata") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```


# Replication, open science and reproducibility

```{r generateTableReplication, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "replication") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Teaching

```{r generateTableTeaching, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "teaching") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# History

```{r generateTableHistory, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "history") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Funny

```{r generateTableFunny, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "funny") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```